Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-03-06 paper/main.tex
setting Discussion to zero
Nelson

We study the alignment of dark matter halos with the cosmic web as described by
the tidal and velocity shear fields. We focus on the alignment of their
shape, angular momentum and peculiar velocities. We use a cosmological N-body
simulation that allows to study dark matter halos spanning almost five orders
of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun over spatial scales
of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the halo shape
and the tidal field web presents the strongest alignment along
filaments and walls with a signal that gets stronger as the halo mass
increases; in the case of the velocity shear only massive halos
$>10^{12}$\hMsun tend to have their shapes be perpendicular to
filaments and walls. For the angular momentum we find alignment
signals only for halos more massive than $10^{12}$\hMsun both in the
tidal and velocity shear webs where the preferences are to be
perpendicular to filaments or parallel to walls,
respectively. Finally, the peculiar velocities show a strong alignment
for all halo masses to move along filaments and walls in the tidal
web, while in the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}$\hMsun. Most of
the different signals between the two web description are due to the
fact that that the main directions of stronger tidal tension and
velocity shear coincide for halos below $10^{12}$\hMpc but are
perpendicular to each other for halos more massive than this
threshold.

@@

There is a long observational tradition stuying galactic properties
as a function of its large scale environment. In these situations the environment
definition is based on quantities easily accesible to observations
such as the number density. With the advenment of large
surveys the visibility of the cosmic web is clear. As a consequence,
in order to capture this filamentarity, the environment definition
started to be more complex, involving shear properties of the galaxy
density field or the reconstructuted dark matter density field.

The emergence of this web like structure is a great success of large
scale structure growth models based on gravitational
instability. Using numerical simulations allows the time description
of such structure together with the formation of the virialized dark
matter halos, which in turn should host observable galaxies. The
finding of gas filaments that feed galaxies is another theoretical
hint that strenghten the expected connection between galactic
properties ant their place in the cosmic web.

Using high resolution simulations it has been stablished that halos of
a given mass for earlier in denser regions; concentration, spin and
shape also depend on the local density. In the last decade new
algorithms have implemented cosmic web classifications that go beyond
the local density by defining a location to be a peak, sheet, filament
or void depending on the simmetry properties of the local dark matter
distribution.

There analytical frameworks, such as tidal torque theory, that
aim at describing how galaxies gain angular momentum and expect a
correlation of this quantity with the cosmic web. The observational
studies that try to measure such correlations actually try to use as a
proxy the observed shape of galaxies. In this respect it is useful to
have a theoretical baseline for the correlations of angular momentum
and shape with the cosmic web.

In the same spirit of describing the place of galaxies within the
cosmic web, there has been an revival of surveys that measure the
cosmic flow patters in the Local Universe. Assuming the correspondence
between the divergenec of the cosmic flow velocity field and the local
matter overdensity (valid in the linear regime) one could construct
accurate maps of the matter density from peculiar velocities. From
this perspective is interesting to look at the expected alignment of
the peculiar velocities.

@@

The structure of this \documentname is the following. In \S
\ref{sec:theory} we present the theoretical antecedendts for the
alignment studies we present in this paper. In \S
\ref{sec:nbody} we present the N-body
cosmological simulation and halo catalogs next to describe in
\S\ref{sec:algorithms} the two web-finding algorithms we use. In
\S\ref{sec:results} we present our main results about the alignment
of shape, spin and peculiar velocities with respect to the cosmic
web. We continue with a discussion of these results in
\S\ref{sec:discussion} paying special attention to resolution effects
and the conditions that might drive the strong alignment signals
observed in the precedent section. In \S\ref{sec:conclusions} we
present our conclusions.

@@

There is abundant literature on the issue of shape and angular momentum
aligmnent of dark matter haloe with respect to the cosmic web. In this
paper we focus our attention on results published during the last
decade that have made use of large N-body dark matter only
cosmological simulations. There are many works that have addressed
this problem using observational data from large surveys such as the
Sloan Digital Sky Survey (SDSS), however we choose to narrow our
discussion to simulation based studies which are prone to comparison.

@@

For an isotropic ditribution of the vector around the direction defined by
$\hat{n}$ the $\mu$ distribution, ranging between $0$ and $1$, should
be flat and its mean value shoud be
$\langle|mu|\rangle=0.5$. If a distribution is biased towards $1$
($\langle\vert\mu\vert\rangle>0.5$) we call this an statistical
alignment along $\hat{n}$, while in the case of a bias towards $0$
($\langle\vert\mu\vert\rangle<0.5$) we talk about an anti-alignment,
meaning an perpendicular orientations with respecto to the $\hat{n}$
direction.

\cite{Trowland2013} presented a parameterization for the $\mu$
distribution in the case of angular momentm alignment based on
theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
the Appendix A). Under this parameterization it was found a unique
correspondece between the full shape of the $\vert\mu\vert$
distribution and its average. In this paper we use that result to only
present the results for the average $\langle\vert\mu\vert\rangle$.

Table 1 and Table 2 summarize recent results found in the literature for
shape and angular momentum alignment. The Appendix A includes a detailed
description of the definitions, algorithms and simulations used in
each one of these studies. In these tables the first column describe
the reference, the second column summarizes the web finding method
with a single name, the third scale associates an spatial scale to the
web finding methods, in most cases it corresponds to the grid size or
smoothing scale used to interpolate the underlying matter density or
velocity field; The fourth column indicates along which web element
(filament or wall) was measured the alignment; the fifth colume
indicates the strenght of the alignment/anti-alignment, $++$/$--$
indicate a strong alignement/anti-alignment while $+$/$-$ indicate a
weaker signal; the last columns indicates whether the described signal
is present within a defined range of halo mass.

@@

In this \documentname we use the Bolshoi simulation that follows the
non-linear evolution of a dark matter density field on cosmological
scales. The volume is a cubic box with 250\hMpc on a side, the matter
density field is sampled with $2048^3$ particles. The  
cosmological parameters in the simulation correspond to the results
inferred from WMAP5 data \citep{2009ApJS..180..306D}, which are also consistent with the more
recent results of WMAP9 \citep{2013ApJS..208...19H}. These parameters are $\Omega_m=0.27$,
$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
matter density, cosmological constant, normalization of the power
spectrum, the slope in the spectrum of the primordial matter
fluctuation and the dimensionless Hubble constant. With this
conditions the mass of each dark matter particle in the simulation
corresponds to $m_p=1.4\times 10^{8}$\hMsun. A more detailed
description of the simulation can be found in
\citep{2011ApJ...740..102K}.

@@

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
%
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
is the matter overdensity, $\bar{\rho}$ is the average matter density,
$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
matter density parameter. A detailed presentation of this algorithm
can be found in \citep{Tweb}.

@@

\begin{equation}
\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
  r_{\alpha}}\right), 
\end{equation}
%
where $v_{\alpha}$ correspond to the components of the peculiar
comoving velocities. With this definition the trace of the shear
tensor is minus the divergence of the velocity field normalized by the
Hubble constant $-\nabla\cdot {\bf}v /H_{0}$. A detailed description
of this algorithm can be found in \citep{Vweb}.

@@

In this paper we compute the cosmic web on cubic grids of two different
resolutions $256^3$ and $512^3$. For the T-Web we interpolate first
the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
smooth using a Gaussian kernel with a spatial variance equal to the
size of one grid cell. This smoothed matter density field is
transformed into Fourier space to solve the Poisson equation and find
the gravitational potential $\phi$. The Hessian is computed a finite
differences method. Finally, the eigenvalues and eigenvectors are
computed on each grid point.

@@

We note that we measure alignments along the eigenvectors of the
cosmic web without defining first whether each point corresponds to a
filament or a wall. Our motivation is two-fold. First, partitioning the
simulation into web elements implies an choice as to what value to use
for the parameter $\lambda_{\rm th}$; although, this has been done
before we consider that

@@

If the halo population does not show any preferential alignment, then
all the halos must be evenly distributed along these three
populations. On the contrary, if there is more than one third of the
halo population in one of these sets, then we can talk about a
preferential alignment along one of the axis. However, this statistic 
does not give a precise answer on the degree of the alignment

@@

We emphasize that all the quantities that we compute in this paper are
independent of any threshold on the eigenvalues that could be used to make a web
clasification into web types. Instead, we focus on the alignments with
respect to the eigenvectors regardless of the web type. In this
context we recall that the eigenvector $\hat{e}_1$ is vector
perpendicular to the plane defining a sheet and also a filamente and
that $\hat{e}_3$ is the vector that marks the direction of a filament
and lies on the plane of a sheet. Therefore we focus on quantifying
the degree of alignment along these two eigenvectors.

This experiment complements the results obtained by the PA satistic by
computing the average and standard deviation of
$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform this
tests in differet populations split into different mass bins
logarithmically spaced between $1\times 10^{9}$\hMsun and
$1\times10^{14}$\hMsun.

@@

@@

The shape alignment and the Vweb (upper row, left column) gives a
different perspective. Firstly, there seems to be little evidence
for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
on the grid resolution. Secondly, the alignment at higher masses goes
along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
perpendicular to the filaments and sheets. In the discussion section
we clarify this result that at first might seem puzzling.

For the angular momentum alignment and the Tweb (middle row, right
column) we find that at low masses $<10^{12}\hMsun$ no evidence for
any alignment. At higher masses $>10^{12}\hMsun$ there is weak signal
of preferential alignment along the first and second eigenvectors,
between $35\%$ to $45\%$ of the halos are aligned with respect to
$\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
of the halos are aligned along respect to $\vec{e}_{3}$. This means
that most of the halos are perpendicular to the filaments and do not
have a clear alignment with respect to walls.

The angular momentum in the Vweb (middle row, left column) presents a
a signal of alignment along the second eigenvector $\hat{e}_{2}$,
between $45\%$ to $60\%$ of the halos are aligned along that
direction. While there is a minority of halos aligned with
$\vec{e}_{1}$.  There a clear change in trends around
$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
below that mass range there is no evidence for alignment while at
higher masses appear all the trends we describe. This means that most
of the halos tend to lie along walls but do not have a clear alignment
with respect to filaments.

The peculiar velocities show a weak but consistent alignment along the
third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
$10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
resolution. $45\%$ of the halos are aligned while only $25\%$ are
aligned along the first eigenvector $\vec{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb show the same trend
but weaker and only for low mass halos $<10^{12}$.

In the next subsections we present a complementary account of this
results by presenting quantitative results of the average angle
between vector pairs describing the alignments discussed so far.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment}} 
\end{figure*}

@@

In the case of the Vweb (left column) we have a clear alignment with
respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
values $\muavg\approx 0.8$ well above the expected value of $0.5$ for
random distribution. With respect to the third eigenvector we measure
an anti-alignment with $\muavg\approx0.3$. For low masses
$<10^{12}\hMsun$ we do not detect any aligmnent signal. This is 
consistent with the PA results of massive halos
perpendicular to filaments and parallel to walls.

The Tweb (right column) show alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude less than the V-web. In this
case we measure an alignment along the third eigenvectors and an
antialignment along the first eigenvector. In the later case at the
highest mases $\muavg\approx 0.8$ while in the former $\muavg\approx
0.2$. This strong alignment/antialignment signal mirrors the
interpretation from the PA results that describe halos lying parallel
both to filaments and walls.

@@

We now take a look at the angular momentum alignment. Figure
\ref{fig:spin_alignment} shows the results as a function of halo mass
following the same panel distributio as in Figure
\ref{fig:shape_alignment}. In all cases we see that these alignment
trends are weaker than shape alignments. For the Vweb low mass halos
$<10^{12}$\hMsun do not show any preferential alignment with the
cosmic web. Halos more massive than this threshold have their angular
momentum slightly perpendicular to the direction defined by the first
eigenvector and uncorrelated to the third eigenvector. This translates
into a weak tendency for the angular momentum to lie parallel to walls.

In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun 
is also absent. More massive halos present a weak alignment along
first eigen vector and anti-alignment with the third eigenvector. This
provides a quantitative expression of the results derived from the
preferential alignment whereby the angular momentum is weakly
perpendicular to filaments.

\subsection{Peculiar velocity Alignment}

@@

Figure \ref{fig:velocity_alignment} shows the results for peculiar
velocities alignments. In the case of the Vweb, the peculiar
velocities show a weak signal of aligmnent ($\muavg\approx0.55$)
along the third eigenvector for low masses $<10^{12}$\Msun and a weak
antialigment at higher masses. The strengt of the alignment also shows
clear dependency on the grid size used to compute the web.

The Tweb shows a stronger alignment with the third eignenvecor at all
masses with $\muavg\approx0.6$ and an antialignment with the first
eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
these trends remain baiscally unchanged at all masses and grid
resolutions, with only minor change for halos masses $>10^{13}$\hMsun.

In the first place we wish to directly compare the results of the two
algorithms. For the two algorithms we have the information for the
eigenvectors and the eigenvalues on exactly the same positions defined
by the grids. This allows us tocompute the pair-wise allignment
between the eigenvectors in the two web finders.

We are mainly interested in the alginment of the web with
the halos. Therefore we restrict our analysis to the grid cells that are
occupied by halos. If we had decided to perform this kind of analysis
on all the grid cells, the statistics would be dominated by the void
regions, because the dominate in number the fraction of cells in the
simuation.

\subsection{Interweb Alignment}

@@

Figure \ref{fig:interweb} shows the values for $\muavg$ between the
two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
shows that there is an alignment, $\muavg\approx 1.0$, for low mass
halos and an antialignment, $\muavg\approx 0.2$ for massive.

@@

On the scale where the halos more massiven than $10^{13}$\hMsun are
located, the relationshop between the velocity shear and the tidal
field changes. There, the fastest momentum-weighted collapse direction
(defined by the V-web) is perpendicular to the direction where the
tidal compression is the highest.

@@

For each mass interval we perform cuts in the following properties:
spin, concentration, triaxiallity, circularity  and density. We
measure the web alignments in two sets, each one including the $30\%$
of halos in the lower/higher end of the corresponding property.

{\bf Possible conclusion. Prolateness follow concentration. In the Tweb
Angular momentum alignment is influenced by spin at higher masses. In
the Vweb angular momentum alginment is influenced by all factors. In
the peculiar velocity alginment only spin seemss to have an effect. }

\begin{figure*}
\includegraphics[width=0.90\textwidth,angle=90]{Fig6.pdf}
\caption{The alignment is always taken with respect to the third eigenvector.}
\end{figure*}
\section{Discussion}
\label{sec:discussion}

We do not find a strong signal for the alignment of spin and the
cosmic web. A significant correlation signal has been recently
measured between the spin and the cosmic vorticity
\citep{Libeskind2013b,Laigle2013}. This two facts are consistent with
spin being produced by the non-symmetric part of the shear and tidal
tensors.

>>>>

We study the alignment of dark matter halos with the cosmic web as described by
the tidal and velocity shear fields. We focus on the alignment of their
shape, angular momentum and peculiar velocities. We use a cosmological N-body
simulation that allows to study dark matter halos spanning almost five orders
of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun {\bf and use} spatial scales
of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the halo shape
and the tidal field web presents the strongest alignment along
filaments and walls with a signal that gets stronger as the halo mass
increases; in the case of the velocity shear only massive halos
$>10^{12}$\hMsun tend to have their shapes %be
 perpendicular to
filaments and walls. For the angular momentum we find alignment
signals only for halos more massive than $10^{12}$\hMsun both in the
tidal and velocity shear webs where the preferences are to be
perpendicular to filaments or parallel to walls,
respectively. Finally, the peculiar velocities show a strong alignment
for all halo masses to move along filaments and walls in the tidal
web, while in the velocity shear the same alignment is present but
weaker and only for halos less massive than $10^{12}$\hMsun. Most of
the different signals between the two web description are due to the
fact that %that 
the main directions of stronger tidal tension and
velocity shear coincide for halos below $10^{12}$\hMpc but are
perpendicular to each other for halos more massive than this
threshold.  {\bf This clearly separates halos into those that live
in sheets and filaments (lower masses) and nodes of the cosmic web.}

@@

There is a long observational tradition stuying galactic properties
as a function of {\bf their} large scale environment. In these situations the environment
definition is {\bf usually} based on quantities easily accesible to observations
such as the number density. With the {\bg advent}%advenment 
of large
surveys the visibility of the cosmic web is clear. As a consequence,
in order to capture this filamentarity, the environment definition
started to be more complex, involving shear properties of the galaxy
density field or the reconstructuted dark matter density field.

The emergence of this web like structure is a great success of large
scale structure growth models based on gravitational
instability. %Using 
Numerical simulations allow the time description
of such structures together with the formation of the virialized dark
matter halos, which in turn should host observable galaxies. The
finding of gas filaments that feed galaxies is another theoretical
hint that strenghtened the expected connection between galactic
properties ant their place in the cosmic web.

{\bf With the aid of} high resolution simulations it has been established that halos of
a given mass form earlier in denser regions; concentration, spin and
shape also depend on the local density. In the last decade new
algorithms have implemented cosmic web classifications that go beyond
the local density by defining a location to be a peak, sheet, filament
or void depending on the simmetry properties of the local dark matter
distribution.

There {\bf are} analytical frameworks, such as tidal torque theory, that
aim at describing how galaxies gain angular momentum and expect a
correlation of this quantity with the cosmic web. The observational
studies that try to measure such correlations actually try to use as a
proxy the observed shape of galaxies. In this respect it is useful to
have a theoretical baseline for the correlations of angular momentum
and shape with the cosmic web.

In the same spirit of describing the place of galaxies within the
cosmic web, there has been an revival of surveys that measure the
cosmic flow patterns in the Local Universe. Assuming the correspondence
between the divergence of the cosmic flow velocity field and the local
matter overdensity (valid in the linear regime) one could construct
accurate maps of the matter density from peculiar velocities. From
this perspective it is interesting to look at the expected alignment of
the peculiar velocities.

@@

The structure of this \documentname is the following. In \S
\ref{sec:theory} we present the theoretical antecedents for the
alignment studies we present in this paper. In \S
\ref{sec:nbody} we present the N-body
cosmological simulation and halo catalogs.  Next, we describe in
\S\ref{sec:algorithms} the two web-finding algorithms we use. In
\S\ref{sec:results} we present our main results about the alignment
of shape, spin and peculiar velocities with respect to the cosmic
web. We continue with a discussion of these results in
\S\ref{sec:discussion} paying special attention to resolution effects
and the conditions that might drive the strong alignment signals
observed in the precedent section. In \S\ref{sec:conclusions} we
present our conclusions.

@@

There is abundant literature on the issue of shape and angular momentum
alignment of dark matter halos with respect to the cosmic web. In this
paper we focus our attention on results published during the last
decade that have made use of large N-body dark matter only
cosmological simulations. There are many works that have addressed
this problem using observational data from large surveys such as the
Sloan Digital Sky Survey (SDSS), however we choose to narrow our
discussion to simulation based studies which are prone to comparison.

@@

For an isotropic ditribution of the vector around the direction defined by
$\hat{n}$ the $\mu$ distribution, ranging between $0$ and $1$, should
be flat and its mean value shoud be
$\langle|mu|\rangle=0.5$. If a distribution is biased towards $1$
($\langle\vert\mu\vert\rangle>0.5$) we call this an statistical
alignment along $\hat{n}$, while in the case of a bias towards $0$
($\langle\vert\mu\vert\rangle<0.5$) we talk about an anti-alignment,
meaning a perpendicular orientation with respect to the $\hat{n}$
direction.

\cite{Trowland2013} presented a parameterization for the $\mu$
distribution in the case of angular momentm alignment based on
theoretical considerations by \cite{Lee2005} (Eq. \ref{eq:distro} in
the Appendix A). Under this parameterization a unique
correspondece was found between the full shape of the $\vert\mu\vert$
distribution and its average. In this paper we follow the lines of their work but
only present the results for the average $\langle\vert\mu\vert\rangle$.

Table 1 and Table 2 summarize recent results found in the literature for
shape and angular momentum alignment. The Appendix A includes a detailed
description of the definitions, algorithms and simulations used in
each one of these studies. In these tables the first column describes
the reference, the second column summarizes the web finding method
with a single name, the third scale associates a spatial scale to the
web finding methods, in most cases it corresponds to the grid size or
smoothing scale used to interpolate the underlying matter density or
velocity field; The fourth column indicates along which web element
(filament or wall) was measured the alignment; the fifth colume
indicates the strenght of the alignment/anti-alignment, $++$/$--$
indicate a strong alignement/anti-alignment while $+$/$-$ indicate a
weaker signal; the last columns indicates whether the described signal
is present within a defined range of halo mass.

@@

In this \documentname we use the Bolshoi simulation that follows the
non-linear evolution of a dark matter density field on cosmological
scales. The volume is a cubic box with 250\hMpc on a side, the matter
density field is sampled with $2048^3$ particles. The  
cosmological parameters in the simulation correspond to the results
inferred from WMAP5 data \citep{2009ApJS..180..306D}, which are also consistent with the more
recent results of WMAP9 \citep{2013ApJS..208...19H}. These parameters are $\Omega_m=0.27$,
$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
matter density, cosmological constant, normalization of the power
spectrum, the slope in the spectrum of the primordial matter
fluctuation and the dimensionless Hubble constant. With these
conditions the mass of each dark matter particle in the simulation
corresponds to $m_p=1.4\times 10^{8}$\hMsun. A more detailed
description of the simulation can be found in
\citep{2011ApJ...740..102K}.

@@

\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial
  r_{\alpha}\partial r_{\beta}}, 
\end{equation}
%
where $\phi$ is the gravitational potential rescaled by a factor $4\pi
G\bar{\rho}=3/2\Omega_m H_{0}^2$ in such a way that the Poission
equation can be written as $\nabla^{2}\phi  = \delta$, where $\delta$
is the matter overdensity, $\bar{\rho}$ is the average matter density,
$H_{0}$ is the Hubble constant at present time and $\Omega_m$ is the
matter density parameter. A detailed presentation of this algorithm
can be found in \cite{Tweb}.

@@

\begin{equation}
\Sigma_{\alpha\beta} = -\frac{1}{2H_{0}}\left(\frac{\partial
  v_{\alpha}}{\partial r_{\beta}}+ \frac{\partial v_{\beta}}{\partial
  r_{\alpha}}\right), 
\end{equation}
%
where $v_{\alpha}$ correspond to the components of the peculiar
comoving velocities. With this definition the trace of the shear
tensor is minus the divergence of the velocity field normalized by the
Hubble constant $-\nabla\cdot {\bf}v /H_{0}$. A detailed description
of this algorithm can be found in \cite{Vweb}.

@@

In this paper we compute the cosmic web on cubic grids of two different
resolutions $256^3$ and $512^3$ that roughly correspond
to scales of $1$ and $0.5$h$^{-1}$Mpc, respectively. For the T-Web we interpolate first
the matter density field using a Cloud-In-Cell (CIC) scheme. Then we
smooth using a Gaussian kernel with a spatial variance equal to the
size of one grid cell. This smoothed matter density field is
transformed into Fourier space to solve the Poisson equation and find
the gravitational potential $\phi$. The Hessian is computed using a finite
differences method. Finally, the eigenvalues and eigenvectors are
computed on each grid point.

@@

We note that we measure alignments along the eigenvectors of the
cosmic web without defining first whether each point corresponds to a
filament or a wall. Our motivation is two-fold. First, partitioning the
simulation into web elements implies a choice as to what value to use
for the parameter $\lambda_{\rm th}$; although, this has been done
before we consider that  COMPLETAR...

@@

If the halo population does not show any preferential alignment, then
all the halos must be evenly distributed along these three
populations. On the contrary, if there is more than one third of the
halo population in one of these sets, then we can talk about a
preferential alignment along one of the axes. However, this statistics
does not give a precise answer on the degree of the alignment

@@

We emphasize that all the quantities that we compute in this paper are
independent of any threshold on the eigenvalues that could be used to make a web
clasification into web types. Instead, we focus on the alignments with
respect to the eigenvectors regardless of the web type. In this
context we recall that the eigenvector $\hat{e}_1$ is vector
perpendicular to the plane defining a sheet and also a filament and
that $\hat{e}_3$ is the vector that marks the direction of a filament
and lies on the plane of a sheet. Therefore we focus on quantifying
the degree of alignment along these two eigenvectors.

This experiment complements the results obtained by the PA satistic by
computing the average and standard deviation of
$\vert\langle\hat{s}\cdot\hat{e}_1\rangle\vert$ and
$\vert\langle\hat{s}\cdot\hat{e}_3\rangle\vert$.  We perform these
tests in different populations split into different mass bins
logarithmically spaced between $1\times 10^{9}$\hMsun and
$1\times10^{14}$\hMsun.

@@

CAMBIE EL ORDEN DE PARRAFOS PARA QUE LA FIGURA SE LEA DE IZQ A DERECHA:

The shape alignment and the Vweb (upper row, left column) gives a
different perspective. Firstly, there seems to be little evidence
for an alignment for masses below $10^{11}-10^{12}\hMsun$, depending
on the grid resolution. Secondly, the alignment at higher masses goes
along the first eigenvector $\vec{e}_{1}$ meaning that they mostly lie
perpendicular to the filaments and sheets. In the discussion section
we clarify this result that at first sight might seem puzzling.

@@

The angular momentum in the Vweb (middle row, left column) presents a
a signal of alignment along the second eigenvector $\hat{e}_{2}$;
between $45\%$ to $60\%$ of the halos are aligned along that
direction, while there is a minority of halos aligned with
$\vec{e}_{1}$.  There is a clear change in trends around
$10^{11}\hMsun-10^{12}\hMsun$ depending on the grid resolution;
below that mass range there is no evidence for alignment while at
higher masses all the trends we describe are aparent. This means that most
of the halos tend to lie along walls but do not have a clear alignment
with respect to filaments.

For the angular momentum alignment and the Tweb (middle row, right
column) we find no evidence for any alighment at low masses $<10^{12}\hMsun$.
At higher masses $>10^{12}\hMsun$ there is a weak signal
of preferential alignment along the first and second eigenvectors;
between $35\%$ to $45\%$ of the halos are aligned with respect to
$\vec{e}_1$ and $\vec{e}_2$. Correspondingly, between $10\%$ to $20\%$
of the halos are aligned along $\vec{e}_{3}$. This means
that most of the halos are perpendicular to the filaments and do not
have a clear alignment with respect to walls.

The peculiar velocities (lower panels) show a weak but consistent alignment along the
third eigenvector $\vec{e}_{3}$ of the Tweb for all masses below
$10^{13.0}\hMsun-10^{13.5}\hMsun$ depending on the grid
resolution. $45\%$ of the halos are aligned this way, while only $25\%$ are
aligned along the first eigenvector $\vec{e}_1$. This suggests that
halos tend to move along filaments and parallel to the walls, except
at higher masses where the alignments get randomized.  In contrast,
the peculiar velocities with respect to the Vweb show the same, although weaker, trend
and only for low mass halos $<10^{12}$.

In the next subsections we present a complementary account of these
results by presenting quantitative results of the average angle
between vector pairs describing the alignments discussed so far.

@@

\begin{figure*}
\includegraphics[width=0.75\textwidth]{Fig2.pdf}
\caption{Median of $\cos\theta$ quantifying the shape alignment for
  the Vweb (left) and the Tweb (right) at two different grid
  resolutions. In the upper (lower) panels the angle $\theta$ is
  measured between the halo major axis and the first (third)
  eigenvector.\label{fig:shape_alignment}.  SUGIERO PONER AMBAS LEYENDAS EN UN SOLO PANEL, SINO PARECE QUE
IZQUIERDA Y DERECHA FUERAN PARA DOS RESOLUCIONES DISTINTAS.} 
\end{figure*}

@@

In the case of the Vweb (left column) we have a clear alignment with
respect to the first eigenvector at high masses $>10^{12}\hMsun$, with
values $\muavg\approx 0.8$ well above the expected value of $0.5$ for a
random distribution. With respect to the third eigenvector we measure
an anti-alignment with $\muavg\approx0.3$. For low masses
$<10^{12}\hMsun$ we do not detect any aligmnent signal. This is 
consistent with the PA results of massive halos
perpendicular to filaments and parallel to walls.

The Tweb (right column) shows alignment trends starting at masses of
$10^{10}$\hMsun, two orders of magnitude below than the V-web. In this
case we measure an alignment along the third eigenvector and an
antialignment along the first eigenvector. In the latter case at the
highest mases $\muavg\approx 0.8$, while in the former $\muavg\approx
0.2$. This strong alignment/antialignment signal mirrors the
interpretation from the PA results that describe halos lying parallel
both to filaments and walls.

@@

We now take a look at the angular momentum alignment. Figure
\ref{fig:spin_alignment} shows the results as a function of halo mass
following the same panel layout as in Figure
\ref{fig:shape_alignment}. In all cases we see that these alignment
trends are weaker than the shape alignments. For the Vweb low mass halos
$<10^{12}$\hMsun do not show any preferential alignment with the
cosmic web. Halos more massive than this threshold have their angular
momentum slightly perpendicular to the direction defined by the first
eigenvector and are uncorrelated with the third eigenvector. This translates
into a weak tendency for the angular momentum to lie parallel to walls.

In the case of the Tweb, the alignment for low mass halos $<10^{12}$\hMsun 
is also absent. More massive halos present a weak alignment along
first eigenvector and anti-alignment with the third eigenvector. This
provides a quantitative expression of the results derived from the
preferential alignment whereby the angular momentum is weakly
perpendicular to filaments.

\subsection{Peculiar Velocity Alignment}

@@

Figure \ref{fig:velocity_alignment} shows the results for peculiar
velocities alignments. In the case of the Vweb, the peculiar
velocities show a weak signal of aligmnent ($\muavg\approx0.55$)
along the third eigenvector for low masses $<10^{12}$\Msun and a weak
antialignment at higher masses. The strength of the alignment also shows
a clear dependency on the grid size used to compute the web.

The Tweb shows a stronger alignment with the third eignenvecor at all
masses with $\muavg\approx0.6$ and an antialignment with the first
eigenvector with $\muavg\approx 0.4$. In contrast to the Vweb results,
these trends remain basically unchanged at all masses and grid
resolutions, with only minor changes for halos masses $>10^{13}$\hMsun.

MOVI EL TITULO DE LA SUBSECCION AQUI, ESTABA DOS PARRAFOS MAS ABAJO, PERO TAMBIEN MODIFIQUE EL TEXTO INICIAL
\subsection{Interweb Alignment}

@@

%We also wish to directly compare the results of the two
%web tensor algorithms. 
For the two algorithms, Tweb and Vweb, we have the information for their
eigenvectors and eigenvalues on exactly the same positions defined
by the grids. This allows us tocompute the pair-wise alignment
between the eigenvectors in the two web finders.

We are mainly interested in the alignment of the web near
halos. Therefore we restrict our analysis to the grid cells that are
occupied by halos. Otherwise, if we decided to perform this kind of analysis
on all the grid cells, the statistics would be dominated by the void
regions, because they dominate in number the fraction of cells in the
simuation.

Figure \ref{fig:interweb} shows the values for $\muavg$ between the
two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
shows that there is an alignment, $\muavg\approx 1.0$, for low mass
halos and an antialignment, $\muavg\approx 0.2$ for massive ones.

@@

On the scale where the halos more massive than $10^{13}$\hMsun are
located, the relationship between the velocity shear and the tidal
field changes. There, the fastest momentum-weighted collapse direction
(defined by the V-web) is perpendicular to the direction where the
tidal compression is the highest.

@@

For each mass interval we perform cuts in the following properties:
halo spin, concentration, halo triaxiallity defined as $(A^2-B^2)/(A^2-C^2)$ with
high (low) triaxiality corresponding to prolate (oblate) shapes, circularity ($C/A$)  and halo
inner density (virial mass divided by volume out to the virial radius). We
measure the web alignments in two sets, each one including the $30\%$
of halos in the lower/higher end of the corresponding property.

Figure \ref{fig:drive} shows the results for the major axes of
the Vweb and Tweb (left and right panels) and the major axis,
the angular momentum vector, and the halo peculiar velocity (top, middle
and bottom panels, respectively).  As here we show the average
of the halo population above the lower mass limit imposed, the halo masses that dominate the
statistics are close to this lower limit $~10^{11}\hMsun$.
We show the result for the Twev and Vweb calculated using the two available
resolutions, but as can be seen in general we find no significant differences in our results.

As can be seen, halos with higher circularity and inner density show
a higher alignment with the Vweb major axes.  The oposite is the case
of haloes with higher concentration, spin and triaxiality.  This trend
is also visible in the angular momentum vs. Vweb major axis alignment only
for the concentration and spin, with little differences evidenced by the
other halo properties.  And the alignment strengthening is somewhat
reversed when comparing the Vweb with the halo peculiar velocity,
with some evidence for a strengthening with lower circularity and
inner density, and a weakening with spin and triaxiality.

On the right panels the trends can also be readily seen.  The Tweb
vs. major axis alignments are stronger for higher circularity,
concentration and inner density, and weaker for higher spins and
triaxialities.  With respect to the angular momentum, the alignment
is weaker for higher circularities, concentrations, inner densities and
spins, and is only strengthened when the triaxiality is higher.
Not much difference is seen in the Tweb vs. halo peculiar velocity
alignments, being this the only regime where there is a clear difference
in influence of halo properties on the alignments with the Tweb and Vweb;
the latter do show important changes on the lower-left panel.
